SCM plan for a troubling company

### 2012-01-11 article.tex

The main idea behind configuration control is to achieve control of changes, what impact they'll have and their costs.

Since this company is relatively small, the extent of CCB and it's usage will be a somewhat limited in contrary to the general idea of a CCB.
The CCB consist of the normal lineup with: chairperson, secretary, members and specialists \cite{daniels}. We will select the project manager
to be the chairman and the secretary will be the configuration manager in the company. The project manager will appoint appropriate people to be
members of the CCB and specilists will be contacted on a ``when needed''-basis.

Not every change will be handled by the CCB in our case

Hur stor ccb?
Hur rigorös CR kontroll?

>>>>

\subsection{The change process}
The main idea behind configuration control is to achieve control of changes, what impact they'll have and their costs.

Since this company is relatively small, the extent of CCB and it's usage will be somewhat limited in contrary to the general idea of a CCB.
The CCB consist of the normal lineup with: chairperson, secretary, members and specialists \cite{daniels}. We will select the project manager
to be the chairman and the secretary will be the configuration manager in the company. The project manager will appoint appropriate people to be
members of the CCB and specialists will be contacted on a ``when needed''-basis. There will likely be one representative from each module with the exception
that some modules representatives will be considered experts instead, so that they will not be needed for each meeting.

The software in our case is as described earlier divided into modules. Each module consists of around five developers and they're all
located in the same working area. The changes made on this level are traced through commit-comments and the discussion is taken within
the group orally.

The CCB are only involved when it comes to changes that cover more than one module (the API between modules is modified).
In the case that the CCB gets involved, it will pretty much handle change requests that traditional way, namely:

\begin{enumerate}
 \item A change is submitted to the SCM-manager.
 \item The SCM-manager decides if this change needs a meeting.
 \item If a meeting is needed, one is planned.
 \item On the meeting the chairman takes input and decide to approve or note depending on the input.
\end{enumerate}

% Hur stor ccb?
% Hur rigorös CR kontroll?
